\begin{thebibliography}{20}

\bibitem{n1} 
A. Wiliem, V. Madasu, W. Boles and P. Yarlagadda. 
\textit{A suspicious behaviour detection using a context space model for smart surveillance systems}. 
Computer Vision and Image Understanding, Elsevier, October 2011.
 
\bibitem{n2} 
M. Elhamod and M. D. Levine.
\textit{Automated Real-Time Detection of Potentially Suspicious Behavior in Public Transport Areas}. 
IEEE Transactions on Intelligent Transportation Systems, vol. 14, no. 2, June 2013.

\bibitem{n3} 
L. M. Fuentes and S. A. Velastin.
\textit{Tracking-based event detection for CCTV systems}. 
Pattern Anal. Appl., vol. 7, no. 4, pp. 356–364, December 2004.

\bibitem{n4} 
M. Elhamod and M. D. Levine.
\textit{A real time semantics-based detection of suspicious activities in public scenes}. 
Proc. 9th Conf. CRV, Toronto, ON, Canada, pp. 268–275, 2012.

\bibitem{n5} 
N. D. Bird, O.Masoud, N. P. Papanikolopoulos, and A. Isaacs.
\textit{Detection of loitering individuals in public transportation areas}. 
IEEE Trans. Intell. Transp. Syst., vol. 6, no. 2, pp. 167–177, June 2005.

\bibitem{n6} 
N. Bird, S. Atev, N. Caramelli, R. Martin, O. Masoud, and N. Papanikolopoulos.
\textit{Real time, online detection of abandoned objects in public areas}. 
Proc. IEEE ICRA, pp. 3775–3780, 2006.

\bibitem{n7} 
C. Mu, J. Xie, W. Yan, T. Liu and P. Li.
\textit{A fast recognition algorithm for suspicious behavior in high definition videos. Multimedia Systems}. 
Vol. 22, Iss. 3, 2016-6, p. 275–285, June 2016.

\bibitem{n8} 
K. Schindler and L. v Gool.
\textit{Action snippets: How many frames does human action recognition require?} 
IEEE Conference on Computer Vision and Pattern Recognition, 2008. CVPR 2008. 

\bibitem{n9} 
A. Gilbert, J. Illingworth and R. Bowden.
\textit{Fast realistic multi-action recognition using mined dense spatio-temporal features}. 
Conference on Computer Vision, 2009 IEEE 12th International, 2009.

\bibitem{n10} 
A. Yao, J. Gall and L. V Gool.
\textit{A Hough Transform-Based Voting Framework for Action Recognition}. 
IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2010.

\bibitem{n11} 
S. Sadanand and J. J. Corso.
\textit{Action Bank: A High-Level Representation of Activity in Video}. 
IEEE Conference on Computer Vision and Pattern Recognition (CVPR), July 2012. 

\bibitem{n12} 
R. Arroyo, J. J. Yebes, L. M. Bergasa, I. G. Daza and J. Almazán.
\textit{Expert video-surveillance system for real-time detection of suspicious behaviors in shopping malls}. 
Expert Systems with Applications, Elsevier, June 2015.

\bibitem{n13} 
T. Zhao and R. Nevatia.
\textit{Tracking multiple humans in crowded environment}. 
Proceedings of the 2004 IEEE Computer Society Conference on Computer Vision and Pattern Recognition, 2004. CVPR 2004., Vol. 2, 2004, p. II–406-II-413 Vol.2, July 2004.

\bibitem{n14} 
B. Wu and R. Nevatia.
\textit{Tracking of Multiple, Partially Occluded Humans based on Static Body Part Detection}. 
IEEE Computer Society Conference on Computer Vision and Pattern Recognition - Volume 1 (CVPR'06), Vol. 1, 2006, p. 951–958, July, 2006.

\bibitem{n15} 
L. Li, W. Huang, I. Y. H. Gu, R. Luo and Q. Tian.
\textit{An efficient sequential approach to tracking multiple objects through crowds for real-time intelligent CCTV systems}. 
IEEE Transactions on Systems, Man and Cybernetics Part B, 38, 1254–1269, July 2008.

\bibitem{n16} 
M. Markou and S. Singh.
\textit{Novelty detection: A review-part 1: Statistical approaches}. 
Sig. Proc. 83, 12, 2481–2497, 2003.

\bibitem{n17} 
M. Markou and S. Singh.
\textit{Novelty detection: A review-part 2: Neural network based approaches}. 
Sig. Proc. 83, 12, 2499–2521, 2003.

\bibitem{n18}
\textit{} 
Crime and CCTV in Australia: Understanding the Relationship

\bibitem{n19} 
EC Funded CAVIAR project/IST 2001 37540.
\\\texttt{http://homepages.inf.ed.ac.uk/rbf/CAVIAR/}

\bibitem{n20} 
S. J. Blunsden, R. B. Fisher.
\textit{The BEHAVE video dataset: ground truthed video for multi-person behavior classification}. 
Annals of the BMVA, Vol 2010(4), pp 1-12, 2010.

\bibitem{n21} 
PETS-ECCV. 2004.
\\\texttt{http://www-prima.imag.fr/PETS04/caviar\_data.html}

\bibitem{n22} 
PETS 2006 Benchmark Data. 2006.
\\\texttt{http://www.cvg.rdg.ac.uk/PETS2006/data.html}
 


\end{thebibliography}
